---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.width = 10, fig.height = 5,
  fig.align = "center",
  fig.path  = "man/Figure/",
  dev = 'svg'
)
```

# Data of "Contributions of anthropogenic warming and urbanization to intensification of heatwaves over China"

## Figure1
`Figure1_data_(observed and modelled HW variation in 1961-2012).rda`

* df_sm: modelled HW characteristics. A data.table with the columns of:
`scenario`, `type_TRS`, `variable`, `year`, `type_region`, `value`, `probs`, `index`, `model`, `mov`.
  - mov: 5 year moving average of HW characteristics

* df_HW.obs: A data.table with the columns of:
`type_data`, `type_region`, `probs`, `year`, `type_TRS`, `variable`, `index`, `value`, `mov`

```{r}
load("data_Figure1_(observed and modelled HW variation in 1961-2012).rda")
df_sm
df_HW.obs
```

## Figure2
`data_Figure2_ECOF.rda`

* d_coef: regression coefficients of finger print
* d_cont: attributable change to each factor

```{r}
load("data_Figure2_ECOF.rda")
d_cont
d_coef
```

## Figure 3
`data_Figure3_HW at different warming levels.rda`

```{r}
load("data_Figure3_HW at different warming levels.rda")
df
```

## Figure 4
`data_Figure4_PR_spatial.rda`

```{r}
load("data_Figure4_PR_spatial.rda")
df
str(poly_clip, 2)
```

How to visualize `df`?
```{r eval=FALSE, include=TRUE}
d_param <- expand.grid(varname = varnames, indice = unique(df$index))[1, ]
temp <- foreach(varname = d_param$varname, indice = d_param$indice,  i = icount(1)) %do% {
    d <- df[variable == varname & index == indice, .SD, .SDcols = as.character(Tinc)] %>% 
        set_colnames(paste0("x", colnames(.)))
    
    scale_factor = ifelse(indice == "FAR", 100, 1)
    unit         = ifelse(indice == "FAR", "%", "")
    
    poly_clip@data <- data.frame(d[info_clip$id, ])*scale_factor
    p <- plot_FPAR(poly_clip, indice, varname, 
                   stat = list(show = FALSE, name=as.character(indice), loc = c(104, 45)),
                   unit = unit,
                   unit.adj = 0.45,
                   show = FALSE,
                   sp.layout = sp_arc_CH.south) # NULL, sp_arc_CH.south
}
```
